### 2014-08-25 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Add plan diagrams; update exterior photos

\noindent Table~\ref{tab:incident_timeline} shows an overview of the timeline of events. A plan view of the structure and the location where the captain collapsed are shown in Fig.~\ref{fig:simp_geom}, and more details of the fire development are provided in the following sections.

@@

The structure involved in this fire incident was a four-story residential building with a flat roof that consisted of a bitumen membrane. The exterior was primarily stucco with large windows on the top three stories on the rear side of the structure. The right side of the structure shared a common fire wall with another residential structure. The structure had a 17.73~m (58~ft) by 6.38~m (21~ft) footprint and a height of 5.9~m (19~ft), as shown in Fig.~\ref{fig:simp_geom}.

@@

% \begin{figure}[!ht]
% \includegraphics[width=6.5in]{../Figures/1st_Floor_Metric} \\
% \includegraphics[width=6.5in]{../Figures/2nd_Floor_Metric}
% \caption[Plan view of first (top) and second (bottom) floor of structure.]{Plan view of first (top) and second (bottom) floor of structure. Stairs and key rooms are identified using measurements collected by NIST.}
% \label{fig:simp_geom}
% \end{figure}

\begin{figure}[!ht]
\includegraphics[width=3.20in]{../Figures/Post_Exterior_Front}
\hfill
\includegraphics[width=3.20in]{../Figures/Post_Exterior_Rear}
\caption{Front (left) and rear (right) exterior of the structure after the incident.}
\label{fig:post_exterior}
\end{figure}

@@

As discussed in Section~\ref{sec:geometry}, the structure had exterior dimensions of 17.73~m (58~ft) by 6.38~m (21~ft) and a total height of 5.9~m (19~ft). To ensure adequately resolved fluid flow in and out of the structure, the computational domain was extended beyond the volume of the structure. The total volume of the computational domain was 17~m (56~ft) by 22~m (72~ft) by 13.6~m (45~ft). A grid resolution of 10~cm (3.9~in) was used, which required approximately 5.1 million computational cells. As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas will snap to the nearest 10~cm. Figure~\ref{fig:geom_grid} shows the front of the structure rendered in Smokeview with the 10~cm mesh. The domain was divided into 16 meshes (each containing between 289,000 and 346,800 grid cells) that could be processed in parallel, which reduced the amount of required calculation time to approximately 3~days. Figure~\ref{fig:mult_mesh} shows the entire structure within the computational domain that has been divided into multiple meshes. Table~\ref{tab:model_parameters} shows a summary of the model input parameters for the simulations that were conducted as part of this study.

>>>>

\noindent Table~\ref{tab:incident_timeline} shows an overview of the timeline of events. A plan view of the structure, the location where the downed firefighters were located, and more details of the fire development are provided in the following section.

@@

The structure involved in this fire incident was a four-story residential building with a flat roof that consisted of a bitumen membrane. The exterior was primarily stucco with large windows on the top three stories on the rear side of the structure. The right side of the structure shared a common fire wall with another residential structure. The structure had a 17.73~m (58~ft) by 8.53~m (28~ft) footprint and a height of 5.9~m (19~ft), as shown in Fig.~\ref{fig:floor_plan}.

@@

\begin{figure}[!ht]
\includegraphics[width=5.0in]{../Figures/Plan_Second_Floor_Metric}
\includegraphics[width=5.0in]{../Figures/Plan_First_Floor_Metric}
\includegraphics[width=5.0in]{../Figures/Plan_Basement_Metric}
\caption[Plan view of second floor (top), first floor (middle), and basement floor (bottom) of structure.]{Plan view of second floor (top), first floor (middle), and basement floor (bottom) of structure. Stairs and rooms are identified using measurements collected by NIST.}
\label{fig:floor_plan}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5.50in]{../Figures/Post_Exterior_Front} \\
\vspace{0.1in}
\includegraphics[width=3.50in]{../Figures/Post_Exterior_Rear}
\caption{Front (top) and rear (bottom) exterior of the structure after the incident.}
\label{fig:post_exterior}
\end{figure}

@@

As discussed in Section~\ref{sec:geometry}, the structure had exterior dimensions of 17.73~m (58~ft) by 8.53~m (28~ft) and a total height of 5.9~m (19~ft). To ensure adequately resolved fluid flow in and out of the structure, the computational domain was extended beyond the volume of the structure. The total volume of the computational domain was 17~m (56~ft) by 22~m (72~ft) by 13.6~m (45~ft). A grid resolution of 10~cm (3.9~in) was used, which required approximately 5.1 million computational cells. As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas will snap to the nearest 10~cm. Figure~\ref{fig:geom_grid} shows the front of the structure rendered in Smokeview with the 10~cm mesh. The domain was divided into 16 meshes (each containing between 289,000 and 346,800 grid cells) that could be processed in parallel, which reduced the amount of required calculation time to approximately 3~days. Figure~\ref{fig:mult_mesh} shows the entire structure within the computational domain that has been divided into multiple meshes. Table~\ref{tab:model_parameters} shows a summary of the model input parameters for the simulations that were conducted as part of this study.
